Blueprint for efficient nuclear spin characterization in color center

### 2024-02-09 article.tex
added some references in the introduction

\begin{abstract}
Nuclear spins in solids offer a promising avenue for developing scalable quantum hardware. Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
However, characterising individual nuclear spin is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored characterization protocols.
While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
We provide a theoretical framework and adapt it for use with color-centers exhibiting various spins. Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix.
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents
\section{Introduction and background}
Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum}, and quantum registers \cite{bradley2019ten}.

@@

To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register.

@@

Also, the protocols also can only be applied to electron spins with a specific spin multiplicity.

>>>>

\begin{abstract}
Nuclear spins in solids offer a promising avenue for developing scalable quantum hardware. Leveraging nearby single-color centers, these spins can be efficiently addressed at the single-site level through spin resonance.
However, characterising individual nuclear spins is quite cumbersome since the utility of characterisation protocols may differ depending on the strength of the hyperfine coupling, necessitating tailored approaches and experimental conditions.
While modified electron spin Hahn echoes like CPMG and XY8 pulse sequences are commonly employed, they encounter significant limitations in scenarios involving spin-1/2 systems, strongly coupled spins, or nuclear spin baths comprising distinct isotopes.
Here, we present a more straightforward approach for determining the hyperfine interactions among each nuclear and the electron spin. 
This method holds promise across diverse platforms, especially for emerging S=1/2 group IV defects in diamond (e.g., SiV, GeV, SnV, PbV) or silicon (T-centre). 
We provide a theoretical framework and adapt it for the use with color-centers exhibiting various spins. Through simulations conducted on nuclear spin clusters, we evaluate different protocols and compare their performance using the Fisher information matrix and Cramer Rao bounds.
\end{abstract}

%\keywords{Suggested keywords}%Use showkeys class option if keyword
                              %display desired
\maketitle
%\tableofcontents
\section{Introduction and background}
Optically active defects in solids, known as color centers, have been utilized in various quantum applications \cite{awschalom2018quantum}, including quantum networks \cite{pompili2021realization}, quantum sensing \cite{degen2017quantum, meinel2023high}, and quantum registers \cite{bradley2019ten, vorobyov2021quantum, hesselmeier2023measuring, hesselmeier2024high}.

@@

To implement efficient quantum control for these memories, it is imperative to have precise knowledge of the full Hamiltonian governing the register \cite{vorobyov2023transition,bradley2022robust}.

@@

Also, the protocols can only be applied to electron spins with a specific spin multiplicity.
